The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S.

### 2023-02-20 outputs/paper/paper.qmd
Update paper.qmd

```{r}
#| label: fig-bills
#| fig-cap: Trend in US Birth Rates
#| echo: false

@@

Talk way more about it.

Figure 3. place it here with the Figure 2-a from the Original paper

```{r}
#| label: fig-billsss
#| fig-cap: Trends in Birth Rates by Population subgroup Five-year age group
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@

# Model

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

@eq-bayes seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

>>>>

```{r}
fig1_data <- read.csv("data/fig_1.csv")
fig1_data %>%
  ggplot(aes(x = year,
             y = brate_all)) +
  geom_line() +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  labs(
    title = "Trend in US Birth Rates",
    x = "Years",
    y = "Births per 1,000 women age 15-44",
    caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019 and 2020."
  )  +
  theme_light()
```

@@

Figure 3. place it here with the Figure 2-a from the Original paper
```{r}
#| label: fig-billsss
#| fig-cap: Trends in Birth Rates by Population subgroup Five-year age group
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@
